Structure Learning for $\VAR(p)$ Models

### 2019-05-16 paper/paper.tex
Updated figures.

\begin{definition}[Graph Theory Review]
  A \textit{graph} $\gcg = (\mathcal{V}, \gcge)$ is simply a
  tuple of sets respectively called \textit{nodes} and \textit{edges}.
  Throughout this paper, we have in all cases
  $V = [n] \defeq \{1, 2, \ldots, n\}$.  We will also focus solely on
  \textit{directed} graphs, where the edges
  $\gcge \subseteq V \times V$ are \textit{ordered} pairs.

>>>>

\begin{definition}[Graph Theory Review]
  A \textit{graph} $\gcg = (V, \gcge)$ is simply a
  tuple of sets respectively called \textit{nodes} and \textit{edges}.
  Throughout this paper, we have in all cases
  $V = [n] \defeq \{1, 2, \ldots, n\}$.  We will also focus solely on
  \textit{directed} graphs, where the edges
  $\gcge \subseteq V \times V$ are \textit{ordered} pairs.
